### 2017-10-18 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Spill point text continued

			\subsubsection{Finding the final spill point of a trap} %\label{sec:spill_leak_finding}
			Regarding dome-shaped anticlinal structures, it can be observed that, geometrically and mathematically, a spill point is a saddle point of the reservoir top surface in 3D. Two examples for such saddle points are visualized in Figures \ref{fig:saddle_point} and \ref{fig:saddle_point_between_maxima}. The latter one in particular, illustrates well

			\begin{figure}[h]
				%\centering
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_point.png}
					\caption{Graph and saddle point of the function $z=x2−y2$.}\label{fig:saddle_point} 
				\end{subfigure}
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_Point_between_maxima.png}
					\caption{Saddle point between two maxima.}\label{fig:saddle_point_between_maxima} 
				\end{subfigure}
				\caption{Two examples for saddle points on surfaces of 3D functions (from Wikimedia Commons)}
			\end{figure}

>>>>

			\subsubsection{Finding the final spill point of a trap} %\label{sec:spill_leak_finding}
			Regarding dome-shaped anticlinal structures, it can be observed that, geometrically and mathematically, a spill point is a saddle point of the reservoir top surface in 3D. SADDLE POINT DEFINITION
			Two examples for such saddle points are visualized in Figure \ref{fig:saddle_points_general}. Particularly Figure \ref{fig:saddle_point_between_maxima} can be seen as a representation of a point of spill between two dome structures (i.e. 3D surface maxima) is defined by the surface's saddle point between both.

			\begin{figure}[h]
				%\centering
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_point.png}
					\caption{Graph and saddle point of the function $z=x2−y2$.}\label{fig:saddle_point} 
				\end{subfigure}
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_Point_between_maxima.png}
					\caption{Saddle point between two maxima.}\label{fig:saddle_point_between_maxima} 
				\end{subfigure}
				\caption{Two examples for saddle points on surfaces of 3D functions (from Wikimedia Commons)}\label{fig:saddle_points_general}
			\end{figure}
